---
title: "Funding Report: Goldberg Gator Engineering Explorers Summer Program 2023"
author: "Krista D. Chisholm"
date: "2023-10-02"
output: 
  html_document:
    theme: paper
    toc: true
    number_section: true
    toc_float:
      collapsed: true
    fig_width: 6
    fig_height: 4
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
summary(cars)
```

```{r pressure, echo=FALSE}
plot(pressure)
```

# Summary

The Goldberg Gator Engineering Explorers (GGEE) Summer Program was designed to provide middle school students with an authentic experience in programming, engineering design, and computational thinking. The 2023 Summer Program successfully engaged 319 students across 8 school districts. Students developed computational thinking skills through design-based challenges using micro:bit micro-controllers. 

Schools and Districts partnered with the GGEE program to host programs and sponsor teachers and materials for the programs at their schools. There were 20 local teachers that lead summer programs in their area. Twenty undergraduate engineering students from the University of Florida and neighboring colleges and universities supported teacher leaders and served as mentors for students in the program. Both teachers and undergraduate mentors were trained in program activities to upskill their abilities in programming, computational thinking, engineering desgin, and teaching practices. Two grant staff coordinated and ran the programs. 

----DATA 

Demographics
How students enjoyed the program
Growth from beginning to end

Follow up after-school programs in 5 districts for 12 sessions with around 200 students participating in the program. 

Program costs per student 

Students reported they felt challenged during the program but were rewarded when their code or design worked. They also mentioned the importance of collaboration with peers to solve engineering problems, and they enjoyed the mentorship of the college students working with the program. The longitudinal effects of the summer program on grades in math and science and students' enrollment in higher-level courses will be tracked by the research study for the program. All districts provided in-kind donations to the camp, and many school districts have plans to host or expand the programs for next year. Some schools have asked about follow-up programming, including afterschool programming to continue student engagement. The cost per student for the program was $996, including all costs for program development (three months), camp costs (two months), and post-assessment of the program. The cost per student for future camps should be less owing to development costs built into the program's first year.


# Introduction

## Background
The Goldberg Gator Engineering Explorers Summer Program was initiated by a generous donor, Arnold Goldberg, to the University of Florida Foundation. He envisioned a free summer program for underrepresented minority middle school students. The program would allow students to experience computer science and have opportunities to learn to not only program but build skills in computational thinking, problem solving, and engineering design. The vision was brought to life by the EQuIPD grant at the University of Florida. Their team has developed introductory and advanced-level summer programs and have worked with schools and districts to host the programs across the state of Florida. 



Provide a brief overview of the middle school summer program, including its purpose and objectives. Highlight why the program was initiated and its importance in the district.

## Purpose of the Report
Explain the purpose of this final report and what the reader can expect to find within it.

# District Recruitment

## Recruitment Strategies
Detail the strategies used to recruit students for the program. Discuss any partnerships or collaborations that helped with recruitment efforts.

## Participant Selection Criteria
Explain the criteria used to select participants for the program. This could include grade level, academic standing, or other factors.

# Program Calendar

## Overview of Program Dates and Activities
Provide an overview of the program's calendar, including the duration of the program, daily schedules, and key activities.

# Program Numbers

## Enrollment Statistics
Present enrollment data, including the number of students who initially registered, and any changes over the course of the program.

## Attendance Records
Share attendance records to illustrate the level of student engagement and participation throughout the program.

## Dropout Rates (if applicable)
If there were any dropouts during the program, provide details and reasons for dropout.

# Student Demographics

## Breakdown of Participant Demographics
Include demographic information such as age, gender, ethnicity, and socioeconomic background of the participating students.

# Pre-Survey Responses

## Summary of Pre-Program Survey Results
Summarize the responses from the pre-program survey, highlighting key findings and insights.

# Survey Responses

## Analysis of Ongoing Survey Data (if conducted during the program)
If you conducted surveys during the program, analyze the responses and share any noteworthy trends or changes over time.

# Student Interviews

## Highlights from Student Interviews
Share significant insights and quotes gathered from student interviews, emphasizing their experiences and perspectives.

# Final Program Survey Responses

## Summary of Post-Program Survey Results
Present the results of the post-program survey, emphasizing any changes in student responses compared to the pre-program survey.

# Program Outcomes

## Assessment of Program Objectives and Goals
Evaluate whether the program met its objectives and goals as outlined in the introduction.

# Challenges and Lessons Learned

## Identification of Challenges Faced
Discuss any challenges encountered during the program's implementation.

## Lessons Learned and Adaptations Made
Share lessons learned from the program's challenges and any adjustments or improvements made as a result.

# Recommendations

## Suggestions for Program Improvement
Provide recommendations for improving the program in future iterations, based on the insights gained.

## Future Directions
Suggest potential directions for the program's growth or expansion.

# Conclusion

## Recap of Program's Successes
Summarize the program's achievements and positive outcomes.

## Reiteration of Impact on Students
Emphasize how the program benefited the participating students and the broader school community.

# Appendices

Include any supplementary materials, such as additional data charts and graphs, the complete survey questions, and interview transcripts.

Please adapt this template to your specific program and add more details and content as needed to create a comprehensive final report for your middle school summer program.



